---
title: "Bootstrapping Diabetes Data to Illuminate Factors"
author: "Jorie Alvis, McKenna Hogan, Cadeon Ott"
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
---

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(knitr)
library(dplyr)
library(simpleboot)
library(boot) 
library(kableExtra)
library(patchwork)
library("cowplot")
library(gridExtra)
library(cowplot)
set.seed(400)
```

## Dataset Overview {.columns-2 .smaller}

We got our dataset from kaggle:

The dataset consisted of health indicators for people with no diabetes, prediabetes, and diabetes.

We chose to work with the varibles HighBP, HighChol, BMI, AnyHealthcare, GenHlth, and Income

High BP, HighChol, and AnyHealthcare were binary while the others werent.

We decided to bootstrap our data because there was a massive difference in sample sizes for the 3 groups of people

Each of us did a different kind of bootsrapping method

```{r KenData, message=FALSE, warning=FALSE, include=FALSE}
#skewed data
diab.data1<- read_csv("../../data/diabetes_012_health_indicators_BRFSS2015.csv")
#unskewed data
diab.data2<- 
  read_csv("../../data/diabetes_binary_5050split_health_indicators_BRFSS2015.csv")
diab.data3<- read_csv("../../data/diabetes_binary_health_indicators_BRFSS2015.csv")

nodiab.only.1<-diab.data1|>
  filter(Diabetes_012==0)|>
  select(HighBP,HighChol,BMI,AnyHealthcare,GenHlth,Income)
prediab.only.1<-diab.data1|>
  filter(Diabetes_012==1)|>
  select(HighBP,HighChol,BMI,AnyHealthcare,GenHlth,Income)
diab.only.1<-diab.data1|>
  filter(Diabetes_012==2)|>
  select(HighBP,HighChol,BMI,AnyHealthcare,GenHlth,Income)
```

<div style="float: right">
```{r echo=FALSE, fig.height=4, fig.width=4, message=FALSE, warning=FALSE}
ggplot(data=diab.data1)+
  geom_bar(aes(x=Diabetes_012), fill="blue")+
  labs(x="indicator",title="Diabetes Data")
```



```{r KenData2, message=FALSE, warning=FALSE, include=FALSE}
#skewed data
diab.data1<- read_csv("../../data/diabetes_012_health_indicators_BRFSS2015.csv")
#unskewed data
diab.data2<- 
  read_csv("../../data/diabetes_binary_5050split_health_indicators_BRFSS2015.csv")
diab.data3<- read_csv("../../data/diabetes_binary_health_indicators_BRFSS2015.csv")

nodiab.only.1<-diab.data1|>
  filter(Diabetes_012==0)|>
  select(HighBP,HighChol,BMI,AnyHealthcare,GenHlth,Income)
prediab.only.1<-diab.data1|>
  filter(Diabetes_012==1)|>
  select(HighBP,HighChol,BMI,AnyHealthcare,GenHlth,Income)
diab.only.1<-diab.data1|>
  filter(Diabetes_012==2)|>
  select(HighBP,HighChol,BMI,AnyHealthcare,GenHlth,Income)
```

```{r new function data, message=FALSE, warning=FALSE, include=FALSE}

HighBP0<-nodiab.only.1$HighBP
HighBP1<-prediab.only.1$HighBP
HighBP2<-diab.only.1$HighBP

HighChol0<-nodiab.only.1$HighChol
HighChol1<-prediab.only.1$HighChol
HighChol2<-diab.only.1$HighChol

BMI0<-nodiab.only.1$BMI
BMI1<-prediab.only.1$BMI
BMI2<-diab.only.1$BMI

AnyHealthcare0<-nodiab.only.1$AnyHealthcare
AnyHealthcare1<-prediab.only.1$AnyHealthcare
AnyHealthcare2<-diab.only.1$AnyHealthcare

GenHlth0<-nodiab.only.1$GenHlth
GenHlth1<-prediab.only.1$GenHlth
GenHlth2<-diab.only.1$GenHlth

Income0<-nodiab.only.1$Income
Income1<-prediab.only.1$Income
Income2<-diab.only.1$Income

```

```{r function, message=FALSE, warning=FALSE, include=FALSE}
diff.means<-function(data0,data1,data2,R){
  
  
  no_pre<- two.boot(data0, data1, "mean", R = R)
  pre_diab<- two.boot(data1, data2, "mean", R = R)
  diab_no<- two.boot(data2, data0, "mean", R = R)
  
  se.no_pre<-sd(no_pre$t)
  se.pre_diab<-sd(pre_diab$t)
  se.diab_no<-sd(diab_no$t)
  
  bias.no_pre<-rep(NA,R)
  bias.pre_diab<-rep(NA,R)
  bias.diab_no<-rep(NA,R)
  for (i in 1:R){
    bias.no_pre[i]<-no_pre$t[i]-no_pre$t0
    bias.pre_diab[i]<-pre_diab$t[i]-pre_diab$t0
    bias.diab_no[i]<-diab_no$t[i]-diab_no$t0
  }
  bias.no_pre<-mean(bias.no_pre)
  bias.pre_diab<-mean(bias.pre_diab)
  bias.diab_no<-mean(bias.diab_no)
  
  boot.no_pre<-boot.ci(no_pre,type=c("perc","basic"))
  boot.pre_diab<-boot.ci(pre_diab,type=c("perc","basic"))
  boot.diab_no<-boot.ci(diab_no,type=c("perc","basic"))
  
  plot.no_pre<-ggplot() +
    geom_histogram(aes(no_pre$t), fill="darkgoldenrod1") +
    geom_segment(aes(y=25,yend=25,x=boot.no_pre$percent[4],
                     xend=boot.no_pre$percent[5], col="percentile"),size=1.5)+
    geom_segment(aes(y=35,yend=35,x=boot.no_pre$basic[4],
                     xend=boot.no_pre$basic[5],col="basic"),size=1.5)+
    xlab("mean(no diabetes) - mean(prediabetes)")
  
  plot.pre_diab<-ggplot() +
    geom_histogram(aes(pre_diab$t),fill="deepskyblue") +
    geom_segment(aes(y=25,yend=25,x=boot.pre_diab$percent[4],
                     xend=boot.pre_diab$percent[5], col="percentile"),size=1.5)+
    geom_segment(aes(y=35,yend=35,x=boot.pre_diab$basic[4],
                     xend=boot.pre_diab$basic[5],col="basic"),size=1.5)+
    xlab("mean(prediabetes) - mean(diabetes)")
  plot.diab_no<-ggplot() +
    geom_histogram(aes(diab_no$t),fill="coral") +
    geom_segment(aes(y=25,yend=25,x=boot.diab_no$percent[4],
                     xend=boot.diab_no$percent[5], col="percentile"),size=1.5)+
    geom_segment(aes(y=35,yend=35,x=boot.diab_no$basic[4],
                     xend=boot.diab_no$basic[5],col="basic"),size=1.5)+
    xlab("mean(diabetes) - mean(no diabetes)")

  mean.no_pre<-mean(no_pre$t)
  mean.pre_diab<-mean(pre_diab$t)
  mean.diab_no<-mean(diab_no$t)
  return(list(plot.no_pre, boot.no_pre,
              plot.pre_diab, boot.pre_diab,
              plot.diab_no, boot.diab_no,
              mean.no_pre,mean.pre_diab,mean.diab_no))
}

```

```{r calling each variable, message=FALSE, warning=FALSE, include=FALSE, cache=T}
HighBP.list<-diff.means(HighBP0,HighBP1,HighBP2,1000)

HighChol.list<-diff.means(HighChol0,HighChol1,HighChol2,1000)

BMI.list<-diff.means(BMI0,BMI1,BMI2,1000)

AnyHealthcare.list<-diff.means(AnyHealthcare0,AnyHealthcare1,AnyHealthcare2,1000)

GenHlth.list<-diff.means(GenHlth0,GenHlth1,GenHlth2,1000)

Income.list<-diff.means(Income0,Income1,Income2,1000)

```


```{r message=FALSE, warning=FALSE, include=FALSE}
no_pre.row1<-c(HighBP.list[[7]],HighBP.list[[2]][["percent"]][[4]],
              HighBP.list[[2]][["percent"]][[5]],
        HighBP.list[[2]][["basic"]][[4]],HighBP.list[[2]][["basic"]][[5]])
no_pre.row2<-c(HighChol.list[[7]],HighChol.list[[2]][["percent"]][[4]],
        HighChol.list[[2]][["percent"]][[5]],
        HighChol.list[[2]][["basic"]][[4]],HighChol.list[[2]][["basic"]][[5]])
no_pre.row3<-c(BMI.list[[7]],BMI.list[[2]][["percent"]][[4]],BMI.list[[2]][["percent"]][[5]],
        BMI.list[[2]][["basic"]][[4]],BMI.list[[2]][["basic"]][[5]])
no_pre.row4<-c(AnyHealthcare.list[[7]],AnyHealthcare.list[[2]][["percent"]][[4]],
        AnyHealthcare.list[[2]][["percent"]][[5]],
        AnyHealthcare.list[[2]][["basic"]][[4]],AnyHealthcare.list[[2]][["basic"]][[5]])
no_pre.row5<-c(GenHlth.list[[7]],GenHlth.list[[2]][["percent"]][[4]],
        GenHlth.list[[2]][["percent"]][[5]],
        GenHlth.list[[2]][["basic"]][[4]],GenHlth.list[[2]][["basic"]][[5]])
no_pre.row6<-c(Income.list[[7]],Income.list[[2]][["percent"]][[4]],
               Income.list[[2]][["percent"]][[5]],
        Income.list[[2]][["basic"]][[4]],Income.list[[2]][["basic"]][[5]])

no_pre.table<-rbind(no_pre.row1,no_pre.row2,no_pre.row3,no_pre.row4,no_pre.row5,no_pre.row6)
rownames(no_pre.table)<-c("HighBP","HighChol","BMI","AnyHealthcare","GenHlth","Income")
colnames(no_pre.table)<-c("mean","low percentile","high percentile","low basic","high basic")
no_pre.kable<-kable(no_pre.table,caption="no-pre",
                    digits=3,format="html",align="c")|>
  kable_paper("hover", full_width = F)

##

pre_diab.row1<-c(HighBP.list[[8]],HighBP.list[[2]][["percent"]][[4]],
              HighBP.list[[4]][["percent"]][[5]],
        HighBP.list[[2]][["basic"]][[4]],HighBP.list[[2]][["basic"]][[5]])
pre_diab.row2<-c(HighChol.list[[8]],HighChol.list[[4]][["percent"]][[4]],
        HighChol.list[[4]][["percent"]][[5]],
        HighChol.list[[4]][["basic"]][[4]],HighChol.list[[4]][["basic"]][[5]])
pre_diab.row3<-c(BMI.list[[8]],BMI.list[[4]][["percent"]][[4]],BMI.list[[4]][["percent"]][[5]],
        BMI.list[[4]][["basic"]][[4]],BMI.list[[4]][["basic"]][[5]])
pre_diab.row4<-c(AnyHealthcare.list[[8]],AnyHealthcare.list[[4]][["percent"]][[4]],
        AnyHealthcare.list[[4]][["percent"]][[5]],
        AnyHealthcare.list[[4]][["basic"]][[4]],AnyHealthcare.list[[2]][["basic"]][[5]])
pre_diab.row5<-c(GenHlth.list[[8]],GenHlth.list[[2]][["percent"]][[4]],
        GenHlth.list[[4]][["percent"]][[5]],
        GenHlth.list[[4]][["basic"]][[4]],GenHlth.list[[4]][["basic"]][[5]])
pre_diab.row6<-c(Income.list[[8]],Income.list[[4]][["percent"]][[4]],
               Income.list[[4]][["percent"]][[5]],
        Income.list[[4]][["basic"]][[4]],Income.list[[4]][["basic"]][[5]])

pre_diab.table<-rbind(pre_diab.row1,pre_diab.row2,pre_diab.row3,
                      pre_diab.row4,pre_diab.row5,pre_diab.row6)
rownames(pre_diab.table)<-c("HighBP","HighChol","BMI","AnyHealthcare","GenHlth","Income")
colnames(pre_diab.table)<-c("mean","low percentile","high percentile","low basic","high basic")
pre_diab.kable<-kable(pre_diab.table,caption="pre-diab",
                    digits=3,format="html",align="c")|>
  kable_paper("hover", full_width = F)

##

diab_no.row1<-c(HighBP.list[[9]],HighBP.list[[6]][["percent"]][[4]],
              HighBP.list[[6]][["percent"]][[5]],
        HighBP.list[[6]][["basic"]][[4]],HighBP.list[[6]][["basic"]][[5]])
diab_no.row2<-c(HighChol.list[[9]],HighChol.list[[6]][["percent"]][[4]],
        HighChol.list[[6]][["percent"]][[5]],
        HighChol.list[[6]][["basic"]][[4]],HighChol.list[[6]][["basic"]][[5]])
diab_no.row3<-c(BMI.list[[9]],BMI.list[[6]][["percent"]][[4]],BMI.list[[6]][["percent"]][[5]],
        BMI.list[[6]][["basic"]][[4]],BMI.list[[6]][["basic"]][[5]])
diab_no.row4<-c(AnyHealthcare.list[[9]],AnyHealthcare.list[[6]][["percent"]][[4]],
        AnyHealthcare.list[[6]][["percent"]][[5]],
        AnyHealthcare.list[[6]][["basic"]][[4]],AnyHealthcare.list[[6]][["basic"]][[5]])
diab_no.row5<-c(GenHlth.list[[9]],GenHlth.list[[6]][["percent"]][[4]],
        GenHlth.list[[6]][["percent"]][[5]],
        GenHlth.list[[6]][["basic"]][[4]],GenHlth.list[[6]][["basic"]][[5]])
diab_no.row6<-c(Income.list[[9]],Income.list[[6]][["percent"]][[4]],
               Income.list[[2]][["percent"]][[5]],
        Income.list[[6]][["basic"]][[4]],Income.list[[6]][["basic"]][[5]])

diab_no.table<-rbind(diab_no.row1,diab_no.row2,diab_no.row3,diab_no.row4,
                     diab_no.row5,diab_no.row6)
rownames(diab_no.table)<-c("HighBP","HighChol","BMI","AnyHealthcare","GenHlth","Income")
colnames(diab_no.table)<-c("mean","low percentile","high percentile","low basic","high basic")
diab_no.kable<-kable(diab_no.table,caption="diab-no",
                    digits=3,format="html",align="c")|>
  kable_paper("hover", full_width = F)

```


## Percentile and Basic Bootstraps

- I analyzed the variables HighBP, HighChol, BMI, AnyHealthcare, GenHlth, 
and Income for differences in means among no diabetes, prediabetes, and diabetes.

- Overall, I found that there was a significant difference in most of the means. The only
means that i didn't see a difference in were some of the AnyHealthcare CI's 

- There was small difference between the CI's for the percentile and basic bootstraps
which matched my findings for small bias


## Tables for means and CI's no - pre
```{r echo=FALSE, fig.height=4, fig.width=3, message=FALSE, warning=FALSE}
no_pre.kable
```
## Tables for means and CI's pre - diab
```{r echo=FALSE, fig.height=4, fig.width=3, message=FALSE, warning=FALSE}
pre_diab.kable
```
## Tables for means and CI's diab - no
```{r echo=FALSE, fig.height=4, fig.width=3, message=FALSE, warning=FALSE}
diab_no.kable
```

## AnyHealthcare No Diabetes and Prediabetes {.columns-2 .smaller}
<div style="float: left">
```{r echo=FALSE, message=FALSE, warning=FALSE}
AnyHealthcare.list[2]
```

<div style="float: left">
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
```{r echo=FALSE, fig.height=3, fig.width=4, message=FALSE, warning=FALSE}
AnyHealthcare.list[1]
```

## AnyHealthcare Prediabetes and Diabetes {.columns-2 .smaller}
<div style="float: left">
```{r echo=FALSE, message=FALSE, warning=FALSE}
AnyHealthcare.list[4]
```
<div style="float: left">
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
```{r echo=FALSE,fig.height=3, fig.width=4, message=FALSE, warning=FALSE}
AnyHealthcare.list[3]
```


## AnyHealthcare Diabetes and No Diabetes {.columns-2 .smaller}

<div style="float: left">
```{r echo=FALSE, message=FALSE, warning=FALSE}
AnyHealthcare.list[6]
```
<div style="float: left">
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
```{r echo=FALSE, fig.height=3, fig.width=4, message=FALSE, warning=FALSE}
AnyHealthcare.list[5]
```



## Income No Diabetes and Prediabetes {.columns-2 .smaller}

<div style="float: left">
```{r echo=FALSE, message=FALSE, warning=FALSE}
HighBP.list[2]
```

<div style="float: left">
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
```{r echo=FALSE, fig.height=3, fig.width=4, message=FALSE, warning=FALSE}
HighBP.list[1]
```

## Income Prediabetes and Diabetes {.columns-2 .smaller}
<div style="float: left">
```{r echo=FALSE, message=FALSE, warning=FALSE}
HighBP.list[4]
```
<div style="float: left">
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
```{r echo=FALSE, fig.height=3, fig.width=4, message=FALSE, warning=FALSE}
HighBP.list[3]
```


## Income Diabetes and No Diabetes {.columns-2 .smaller}

<div style="float: left">
```{r echo=FALSE, message=FALSE, warning=FALSE}
HighBP.list[6]
```
<div style="float: left">
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
```{r echo=FALSE,fig.height=3, fig.width=4, message=FALSE, warning=FALSE}
HighBP.list[5]
```



```{r JorDataInit, message=FALSE, warning=FALSE, include=FALSE}
# This data has three classes
## No-diabetes: Most observations
## Pre-diabetes: Least observations
## Diabetes: Response of importance
data.main = read_csv("../../data/diabetes_012_health_indicators_BRFSS2015.csv")
data.main = data.main %>% rename("Diabetes"="Diabetes_012")

# Binary Classification
## Same number of observations for no-diabetes and pre-diabetes/diabetes
data.balanced = read_csv("../../data/diabetes_binary_5050split_health_indicators_BRFSS2015.csv")
data.balanced = data.balanced %>% rename("Diabetes"="Diabetes_binary")

# Binary Classification
## More observations of no-diabetes than pre-diabetes/diabetes
data.binary = read_csv("../../data/diabetes_binary_health_indicators_BRFSS2015.csv")
data.binary = data.binary %>% rename("Diabetes"="Diabetes_binary")
```

```{r JorFuncs, message=FALSE, warning=FALSE, include=FALSE}
bootSample = function(data, m, n) {
  ret = list()
  for (i in 1:m) {
    sample.no_d = sample(1:length(data[data$Diabetes == 0,]), size=n, replace=TRUE)
    data.sample.no_d = data[data$Diabetes == 0,][sample.no_d,]
    
    sample.pre_d = sample(1:length(data[data$Diabetes == 1,]), size=n, replace=TRUE)
    data.sample.pre_d = data[data$Diabetes == 1,][sample.pre_d,]
    
    sample.d = sample(1:length(data[data$Diabetes == 2,]), size=n, replace=TRUE)
    data.sample.d = data[data$Diabetes == 2,][sample.d,]
    
    data.sample = rbind(data.sample.no_d, data.sample.pre_d, data.sample.d)
    
    ret[[i]] = data.sample
  }
  
  return(ret)
}

normal_boot = function(data_list, factors) {
  # For each factor of interest
  ret = list()
  for (col_name in factors) {
    # For no, pre, and diabetes
    combo = list()
    for (d in 0:2) {
      data.stats = setNames(data.frame(matrix(ncol = 4, nrow = length(data_list))),
                            c("mean", "sd", "lower", "upper"))
      # For each sample
      for (i in 1:length(data_list)) {
        data.sample = data_list[[i]] %>% filter(Diabetes==d) %>% pull(col_name)
        
        data.mean = mean(data.sample)
        data.sd = sd(data.sample)
        
        delta = pnorm((1-0.95/2))*data.sd
        data.lower = data.mean-delta
        data.upper = data.mean+delta
        
        data.stats[i,] = c(data.mean, data.sd, data.lower, data.upper)
      }
      theta.hat = mean(data.stats$mean)
      theta.se = sd(data.stats$mean)
      
      delta = pnorm((1-0.95/2))*theta.se
      theta.lower = theta.hat-delta
      theta.upper = theta.hat+delta
      
      data.stats[length(data_list)+1,] = c(theta.hat, theta.se, theta.lower, theta.upper)
      
      combo[[d+1]] = data.stats
    }
    ret[[col_name]] = combo
  }
  return(ret)
}

student_t_boot = function(data_list, factors) {
  # For each factor of interest
  ret = list()
  for (col_name in factors) {
    # For no, pre, and diabetes
    combo = list()
    for (d in 0:2) {
      # Theta hat for the whole dataset
      data.theta_hat = mean(data.main %>% filter(Diabetes==d) %>% pull(col_name))
      
      data.stats = setNames(data.frame(matrix(ncol = 5, nrow = length(data_list))),
                            c("mean", "se", "t_stat", "lower", "upper"))
      # For each sample
      for (i in 1:length(data_list)) {
        data.sample = data_list[[i]] %>% filter(Diabetes==d) %>% pull(col_name)
        
        # re-sampled data
        data.resample = data.frame(matrix(ncol=length(data.sample)+1, nrow=length(data_list)))
        for (r in 1:length(data_list)){
          resample = sample(data.sample, size=length(data.sample), replace=TRUE)
          data.resample[r,] = cbind(resample, mean(resample))
        }
        data.mean = mean(data.sample)
        data.se = sd(data.resample[,length(data.sample)+1])
        
        data.t_stat = (data.mean-data.theta_hat)/data.se
        
        data.stats[i,] = c(data.mean, data.se, data.t_stat, NA, NA)
      }
      theta.hat = mean(data.stats$mean)
      theta.se = sd(data.stats$mean)
      
      theta.t_stat = (theta.hat-data.theta_hat)/theta.se
      
      theta.lower = theta.hat-abs(quantile(data.stats$t_stat, probs=c(0.05/2))*theta.se)
      theta.upper = theta.hat+abs(quantile(data.stats$t_stat, probs=c(1-0.05/2))*theta.se)
      
      data.stats[length(data_list)+1,] = c(theta.hat, theta.se, theta.t_stat,
                                           theta.lower, theta.upper)
      
      combo[[d+1]] = data.stats
    }
    ret[[col_name]] = combo
  }
  return(ret)
}
```

```{r JorAnalysisInit, message=FALSE, warning=FALSE, cache=TRUE, include=FALSE}
# The "m"s we are testing
m_list = c(10,30,50,100,250)
# The "n"s we are testing
n_list = c(10,25,75,125,250)
# Factors of interest
factors_list = c("Income", "BMI", "GenHlth", "HighBP", "AnyHealthcare")

ALL_DATA_norm = list(list(), list(), list(), list(), list())
ALL_DATA_stud = list(list(), list(), list(), list(), list())
for (i in 1:5) {
  m = m_list[i]
  for (j in 1:5) {
    n = n_list[j]
    
    boot_data1 = bootSample(data.main, m, n)
    boot_data2 = bootSample(data.main, m, n)
    ALL_DATA_norm[[i]][[j]] = normal_boot(boot_data1, factors_list)
    ALL_DATA_stud[[i]][[j]] = student_t_boot(boot_data2, factors_list)
  }
}
```

## Standard Normal Bootstrap CI

 - We used a Standard Normal Bootstrap for each classification, (No Diabetes, Pre-Diabetes, and Diabetes), and pulled out our factors of interest, (Income, BMI, GenHlth, HighBP, and AnyHealthcare).

 - We also used different values of sample size, `n`, and number of samples, `m`, to showcase the power of bootstrapping with Normal distributions
 
### Assumptions:

 - Need $\hat{\theta}\sim N(E[\hat{\theta}],\,\hat{\text{se}}(\hat{\theta})^2)$
 
 - Need $\hat{\theta}$ to be unbiased
 
 - Large sample size

## Pairs of `m` and `n` values
Tables of standard error of our estimators

```{r echo=FALSE, message=FALSE, warning=FALSE}
pos_list = c("float_left", "float_left", "left")
title_list = c("No Diabetes", "Pre-Diabetes", "Diabetes")

TABLES_norm = list()
TABLES_stud = list()
for (factor.name in factors_list) {
  for (d in 1:3) {
    MEANS_norm = matrix(nrow=5,ncol=5)
    MEANS_stud = matrix(nrow=5,ncol=5)
    SE_norm = matrix(nrow=5,ncol=5)
    SE_stud = matrix(nrow=5,ncol=5)
    for (i in 1:5) {
      for (j in 1:5) {
        MEANS_norm[i,j] = tail(ALL_DATA_norm[[i]][[j]][[factor.name]][[d]]$mean,1)
        MEANS_stud[i,j] = tail(ALL_DATA_stud[[i]][[j]][[factor.name]][[d]]$mean,1)
        SE_norm[i,j] = tail(ALL_DATA_norm[[i]][[j]][[factor.name]][[d]]$sd,1)
        SE_stud[i,j] = tail(ALL_DATA_stud[[i]][[j]][[factor.name]][[d]]$se,1)
      }
    }
    t_title = paste(factor.name, title_list[d], sep=" and ")
    
    # Tables for standard normal
    ############################
    rownames(SE_norm) = paste("m=",m_list,sep="")
    colnames(SE_norm) = paste("n=",n_list,sep="")
    
    means_norm_table = kable(SE_norm, caption=t_title, digits=3, format = "html") %>%
      kable_styling(full_width=F, position=pos_list[d], font_size=8) %>%
      row_spec(0, bold=T, font_size=14) %>% row_spec(0:5, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "3.5em") %>%
      column_spec(2:6, width = "1em") %>% row_spec(c(1,3,5), color="white", background="grey")
    
    TABLES_norm[[factor.name]][[d]] = means_norm_table
    
    # Tables for student t normal
    ############################
    rownames(SE_stud) = paste("m=",m_list,sep="")
    colnames(SE_stud) = paste("n=",n_list,sep="")
    
    means_stud_table = kable(SE_stud, caption=t_title, digits=3, format = "html") %>%
      kable_styling(full_width=F, position=pos_list[d], font_size=8) %>%
      row_spec(0, bold=T, font_size=14) %>% row_spec(0:5, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "3.5em") %>%
      column_spec(2:6, width = "1em") %>% row_spec(c(1,3,5), color="white", background="grey")
    
    TABLES_stud[[factor.name]][[d]] = means_stud_table
  }
}
TABLES_norm[["Income"]][[1]]
TABLES_norm[["Income"]][[2]]
TABLES_norm[["Income"]][[3]]

TABLES_norm[["HighBP"]][[1]]
TABLES_norm[["HighBP"]][[2]]
TABLES_norm[["HighBP"]][[3]]

TABLES_norm[["AnyHealthcare"]][[1]]
TABLES_norm[["AnyHealthcare"]][[2]]
TABLES_norm[["AnyHealthcare"]][[3]]
```

## Bootstrap t CI

 - We used Student-t Bootstraping for each classification, (No Diabetes, Pre-Diabetes, and Diabetes), and pulled out our factors of interest, (Income, BMI, GenHlth, HighBP, and AnyHealthcare).

 - We also used different values of sample size, `n`, and number of samples, `m`, to showcase the difference of double bootstrapping with Student-t distributions
 
 - We wanted to show that larger and more samples decreased our standard error of our estimator
 
### Assumptions:

 - Small bias and skewness of $\hat{\theta}$
 
 - Need $\hat{\theta}$ independent of $\hat{\text{se}}(\hat{\theta})$

```{r message=FALSE, warning=FALSE, include=FALSE}
BOOT.norm = ALL_DATA_norm[[5]][[5]]
BOOT.stud = ALL_DATA_stud[[5]][[5]]
```

## Pairs of `m` and `n` values
Tables of standard error of our estimators

```{r echo=FALSE, message=FALSE, warning=FALSE}
TABLES_stud[["Income"]][[1]]
TABLES_stud[["Income"]][[2]]
TABLES_stud[["Income"]][[3]]

TABLES_stud[["HighBP"]][[1]]
TABLES_stud[["HighBP"]][[2]]
TABLES_stud[["HighBP"]][[3]]

TABLES_stud[["AnyHealthcare"]][[1]]
TABLES_stud[["AnyHealthcare"]][[2]]
TABLES_stud[["AnyHealthcare"]][[3]]
```

## Income

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Tables for m=250, n=250 ###
# Normal CI table
norm_income_table = rbind("No Diabetes"=tail(BOOT.norm$Income[[1]],1)[,-2],
                          "Pre-Diabetes"=tail(BOOT.norm$Income[[2]],1)[,-2],
                          "Diabetes"=tail(BOOT.norm$Income[[3]],1)[,-2])

norm_income_kable = kable(norm_income_table, caption="Normal CI on Income",
                          digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

# Student t table
stud_income_table = rbind("No Diabetes"=tail(BOOT.stud$Income[[1]],1)[,-c(2,3)],
                          "Pre-Diabetes"=tail(BOOT.stud$Income[[2]],1)[,-c(2,3)],
                          "Diabetes"=tail(BOOT.stud$Income[[3]],1)[,-c(2,3)])

stud_income_kable = kable(stud_income_table, caption="Student-t CI on Income",
                          digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

norm_income_kable
stud_income_kable
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
income.norm = rbind(cbind("Diabetes"=rep(0,251),"Income"=BOOT.norm[["Income"]][[1]]$mean),
                    cbind("Diabetes"=rep(1,251),"Income"=BOOT.norm[["Income"]][[2]]$mean),
                    cbind("Diabetes"=rep(2,251),"Income"=BOOT.norm[["Income"]][[3]]$mean))
income.norm = as.data.frame(income.norm)
income.norm$Diabetes = as.factor(income.norm$Diabetes)

income.norm.CIspace = seq(0.5, 4, length.out=3)
income_norm_plot = ggplot() +
  geom_histogram(aes(x=income.norm$Income, y=..count../sum(..count..)*100,
                     fill=income.norm$Diabetes), position="identity", bins=35) +
  geom_segment(aes(x=norm_income_table$lower, xend=norm_income_table$upper,
                   y=income.norm.CIspace, yend=income.norm.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=norm_income_table$mean, xend=norm_income_table$mean,
                   y=income.norm.CIspace-0.1, yend=income.norm.CIspace+0.1),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Normal CI on Income", x="Income", y="Frequency", fill="Diabetes")

#########################
income.stud = rbind(cbind("Diabetes"=rep(0,251),"Income"=BOOT.stud[["Income"]][[1]]$mean),
                    cbind("Diabetes"=rep(1,251),"Income"=BOOT.stud[["Income"]][[2]]$mean),
                    cbind("Diabetes"=rep(2,251),"Income"=BOOT.stud[["Income"]][[3]]$mean))
income.stud = as.data.frame(income.stud)
income.stud$Diabetes = as.factor(income.stud$Diabetes)

income.stud.CIspace = seq(1,6, length.out=3)
income_stud_plot = ggplot() +
  geom_histogram(aes(x=income.stud$Income, y=..count../sum(..count..)*100,
                     fill=income.stud$Diabetes), position="identity", bins=35) +
  geom_segment(aes(x=stud_income_table$lower, xend=stud_income_table$upper,
                   y=income.stud.CIspace, yend=income.stud.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=stud_income_table$mean, xend=stud_income_table$mean,
                   y=income.stud.CIspace-0.1, yend=income.stud.CIspace+0.1),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Student-t CI on Income", x="Income", y="Frequency", fill="Diabetes")

income_norm_plot + income_stud_plot + plot_layout(ncol = 2, guides = "collect")
```

## BMI

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Tables for m=250, n=250 ###
# Normal CI table
norm_BMI_table = rbind("No Diabetes"=tail(BOOT.norm$BMI[[1]],1)[,-2],
                          "Pre-Diabetes"=tail(BOOT.norm$BMI[[2]],1)[,-2],
                          "Diabetes"=tail(BOOT.norm$BMI[[3]],1)[,-2])

norm_BMI_kable = kable(norm_BMI_table, caption="Normal CI on BMI",
                          digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

# Student t table
stud_BMI_table = rbind("No Diabetes"=tail(BOOT.stud$BMI[[1]],1)[,-c(2,3)],
                          "Pre-Diabetes"=tail(BOOT.stud$BMI[[2]],1)[,-c(2,3)],
                          "Diabetes"=tail(BOOT.stud$BMI[[3]],1)[,-c(2,3)])

stud_BMI_kable = kable(stud_BMI_table, caption="Student-t CI on BMI",
                          digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

norm_BMI_kable
stud_BMI_kable
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
BMI.norm = rbind(cbind("Diabetes"=rep(0,251),"BMI"=BOOT.norm[["BMI"]][[1]]$mean),
                    cbind("Diabetes"=rep(1,251),"BMI"=BOOT.norm[["BMI"]][[2]]$mean),
                    cbind("Diabetes"=rep(2,251),"BMI"=BOOT.norm[["BMI"]][[3]]$mean))
BMI.norm = as.data.frame(BMI.norm)
BMI.norm$Diabetes = as.factor(BMI.norm$Diabetes)

BMI.norm.CIspace = seq(1, 7, length.out=3)
BMI_norm_plot = ggplot() +
  geom_histogram(aes(x=BMI.norm$BMI, y=..count../sum(..count..)*100,
                     fill=BMI.norm$Diabetes), position="identity",bins=35) +
  geom_segment(aes(x=norm_BMI_table$lower, xend=norm_BMI_table$upper,
                   y=BMI.norm.CIspace, yend=BMI.norm.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=norm_BMI_table$mean, xend=norm_BMI_table$mean,
                   y=BMI.norm.CIspace-0.15, yend=BMI.norm.CIspace+0.15),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Normal CI on BMI", x="BMI", y="Frequency", fill="Diabetes")

#########################
BMI.stud = rbind(cbind("Diabetes"=rep(0,251),"BMI"=BOOT.stud[["BMI"]][[1]]$mean),
                    cbind("Diabetes"=rep(1,251),"BMI"=BOOT.stud[["BMI"]][[2]]$mean),
                    cbind("Diabetes"=rep(2,251),"BMI"=BOOT.stud[["BMI"]][[3]]$mean))
BMI.stud = as.data.frame(BMI.stud)
BMI.stud$Diabetes = as.factor(BMI.stud$Diabetes)

BMI.stud.CIspace = seq(1, 10, length.out=3)
BMI_stud_plot = ggplot() +
  geom_histogram(aes(x=BMI.stud$BMI, y=..count../sum(..count..)*100,
                     fill=BMI.stud$Diabetes), position="identity", bins=35) +
  geom_segment(aes(x=stud_BMI_table$lower, xend=stud_BMI_table$upper,
                   y=BMI.stud.CIspace, yend=BMI.stud.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=stud_BMI_table$mean, xend=stud_BMI_table$mean,
                   y=BMI.stud.CIspace-0.15, yend=BMI.stud.CIspace+0.15),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Student-t CI on BMI", x="BMI", y="Frequency", fill="Diabetes")

BMI_norm_plot + BMI_stud_plot + plot_layout(ncol = 2, guides = "collect")
```

## GenHlth

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Tables for m=250, n=250 ###
# Normal CI table
norm_GenHlth_table = rbind("No Diabetes"=tail(BOOT.norm$GenHlth[[1]],1)[,-2],
                          "Pre-Diabetes"=tail(BOOT.norm$GenHlth[[2]],1)[,-2],
                          "Diabetes"=tail(BOOT.norm$GenHlth[[3]],1)[,-2])

norm_GenHlth_kable = kable(norm_GenHlth_table, caption="Normal CI on GenHlth",
                          digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

# Student t table
stud_GenHlth_table = rbind("No Diabetes"=tail(BOOT.stud$GenHlth[[1]],1)[,-c(2,3)],
                          "Pre-Diabetes"=tail(BOOT.stud$GenHlth[[2]],1)[,-c(2,3)],
                          "Diabetes"=tail(BOOT.stud$GenHlth[[3]],1)[,-c(2,3)])

stud_GenHlth_kable = kable(stud_GenHlth_table, caption="Student-t CI on GenHlth",
                          digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

norm_GenHlth_kable
stud_GenHlth_kable
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
GenHlth.norm = rbind(cbind("Diabetes"=rep(0,251),"GenHlth"=BOOT.norm[["GenHlth"]][[1]]$mean),
                    cbind("Diabetes"=rep(1,251),"GenHlth"=BOOT.norm[["GenHlth"]][[2]]$mean),
                    cbind("Diabetes"=rep(2,251),"GenHlth"=BOOT.norm[["GenHlth"]][[3]]$mean))
GenHlth.norm = as.data.frame(GenHlth.norm)
GenHlth.norm$Diabetes = as.factor(GenHlth.norm$Diabetes)

GenHlth.norm.CIspace = seq(1, 6, length.out=3)
GenHlth_norm_plot = ggplot() +
  geom_histogram(aes(x=GenHlth.norm$GenHlth, y=..count../sum(..count..)*100,
                     fill=GenHlth.norm$Diabetes), position="identity", bins=35) +
  geom_segment(aes(x=norm_GenHlth_table$lower, xend=norm_GenHlth_table$upper,
                   y=GenHlth.norm.CIspace, yend=GenHlth.norm.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=norm_GenHlth_table$mean, xend=norm_GenHlth_table$mean,
                   y=GenHlth.norm.CIspace-0.1, yend=GenHlth.norm.CIspace+0.1),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Normal CI on GenHlth", x="GenHlth", y="Frequency", fill="Diabetes")

#########################
GenHlth.stud = rbind(cbind("Diabetes"=rep(0,251),"GenHlth"=BOOT.stud[["GenHlth"]][[1]]$mean),
                    cbind("Diabetes"=rep(1,251),"GenHlth"=BOOT.stud[["GenHlth"]][[2]]$mean),
                    cbind("Diabetes"=rep(2,251),"GenHlth"=BOOT.stud[["GenHlth"]][[3]]$mean))
GenHlth.stud = as.data.frame(GenHlth.stud)
GenHlth.stud$Diabetes = as.factor(GenHlth.stud$Diabetes)

GenHlth.stud.CIspace = seq(1, 6, length.out=3)
GenHlth_stud_plot = ggplot() +
  geom_histogram(aes(x=GenHlth.stud$GenHlth, y=..count../sum(..count..)*100,
                     fill=GenHlth.stud$Diabetes), position="identity", bins=35) +
  geom_segment(aes(x=stud_GenHlth_table$lower, xend=stud_GenHlth_table$upper,
                   y=GenHlth.stud.CIspace, yend=GenHlth.stud.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=stud_GenHlth_table$mean, xend=stud_GenHlth_table$mean,
                   y=GenHlth.stud.CIspace-0.15, yend=GenHlth.stud.CIspace+0.15),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Student-t CI on GenHlth", x="GenHlth", y="Frequency", fill="Diabetes")

GenHlth_norm_plot + GenHlth_stud_plot + plot_layout(ncol = 2, guides = "collect")
```

## HighBP

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Tables for m=250, n=250 ###
# Normal CI table
norm_HighBP_table = rbind("No Diabetes"=tail(BOOT.norm$HighBP[[1]],1)[,-2],
                          "Pre-Diabetes"=tail(BOOT.norm$HighBP[[2]],1)[,-2],
                          "Diabetes"=tail(BOOT.norm$HighBP[[3]],1)[,-2])

norm_HighBP_kable = kable(norm_HighBP_table, caption="Normal CI on HighBP",
                          digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

# Student t table
stud_HighBP_table = rbind("No Diabetes"=tail(BOOT.stud$HighBP[[1]],1)[,-c(2,3)],
                          "Pre-Diabetes"=tail(BOOT.stud$HighBP[[2]],1)[,-c(2,3)],
                          "Diabetes"=tail(BOOT.stud$HighBP[[3]],1)[,-c(2,3)])

stud_HighBP_kable = kable(stud_HighBP_table, caption="Student-t CI on HighBP",
                          digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

norm_HighBP_kable
stud_HighBP_kable
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
HighBP.norm = rbind(cbind("Diabetes"=rep(0,251),"HighBP"=BOOT.norm[["HighBP"]][[1]]$mean),
                    cbind("Diabetes"=rep(1,251),"HighBP"=BOOT.norm[["HighBP"]][[2]]$mean),
                    cbind("Diabetes"=rep(2,251),"HighBP"=BOOT.norm[["HighBP"]][[3]]$mean))
HighBP.norm = as.data.frame(HighBP.norm)
HighBP.norm$Diabetes = as.factor(HighBP.norm$Diabetes)

HighBP.norm.CIspace = seq(1, 8, length.out=3)
HighBP_norm_plot = ggplot() +
  geom_histogram(aes(x=HighBP.norm$HighBP, y=..count../sum(..count..)*100,
                     fill=HighBP.norm$Diabetes), position="identity", bins=35) +
  geom_segment(aes(x=norm_HighBP_table$lower, xend=norm_HighBP_table$upper,
                   y=HighBP.norm.CIspace, yend=HighBP.norm.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=norm_HighBP_table$mean, xend=norm_HighBP_table$mean,
                   y=HighBP.norm.CIspace-0.15, yend=HighBP.norm.CIspace+0.15),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Normal CI on HighBP", fill="Diabetes",
       x="HighBP", y="Frequency")

#########################
HighBP.stud = rbind(cbind("Diabetes"=rep(0,251),"HighBP"=BOOT.stud[["HighBP"]][[1]]$mean),
                    cbind("Diabetes"=rep(1,251),"HighBP"=BOOT.stud[["HighBP"]][[2]]$mean),
                    cbind("Diabetes"=rep(2,251),"HighBP"=BOOT.stud[["HighBP"]][[3]]$mean))
HighBP.stud = as.data.frame(HighBP.stud)
HighBP.stud$Diabetes = as.factor(HighBP.stud$Diabetes)

HighBP.stud.CIspace = seq(1, 8, length.out=3)
HighBP_stud_plot = ggplot() +
  geom_histogram(aes(x=HighBP.stud$HighBP, y=..count../sum(..count..)*100,
                     fill=HighBP.stud$Diabetes), position="identity", bins=35) +
  geom_segment(aes(x=stud_HighBP_table$lower, xend=stud_HighBP_table$upper,
                   y=HighBP.stud.CIspace, yend=HighBP.stud.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=stud_HighBP_table$mean, xend=stud_HighBP_table$mean,
                   y=HighBP.stud.CIspace-0.15, yend=HighBP.stud.CIspace+0.15),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Student-t CI on HighBP", fill="Diabetes",
       x="HighBP", y="Frequency")

HighBP_norm_plot + HighBP_stud_plot + plot_layout(ncol = 2, guides = "collect")
```

## AnyHealthcare

```{r echo=FALSE, message=FALSE, warning=FALSE}
### Tables for m=250, n=250 ###
# Normal CI table
norm_AnyHealthcare_table = rbind("No Diabetes"=tail(BOOT.norm$AnyHealthcare[[1]],1)[,-2],
                          "Pre-Diabetes"=tail(BOOT.norm$AnyHealthcare[[2]],1)[,-2],
                          "Diabetes"=tail(BOOT.norm$AnyHealthcare[[3]],1)[,-2])

norm_AnyHealthcare_kable = kable(norm_AnyHealthcare_table,
                                 caption="Normal CI on AnyHealthcare",
                                 digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

# Student t table
stud_AnyHealthcare_table = rbind("No Diabetes"=tail(BOOT.stud$AnyHealthcare[[1]],1)[,-c(2,3)],
                          "Pre-Diabetes"=tail(BOOT.stud$AnyHealthcare[[2]],1)[,-c(2,3)],
                          "Diabetes"=tail(BOOT.stud$AnyHealthcare[[3]],1)[,-c(2,3)])

stud_AnyHealthcare_kable = kable(stud_AnyHealthcare_table,
                                 caption="Student-t CI on AnyHealthcare",
                                 digits=3, format = "html") %>%
      kable_styling("striped", full_width=F, position="float_left", font_size=10) %>%
      row_spec(0, bold = TRUE, font_size=14, align="c") %>% row_spec(0:3, align="c") %>%
      column_spec(1, bold = TRUE, border_right = TRUE, width = "7em")

norm_AnyHealthcare_kable
stud_AnyHealthcare_kable
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
AnyHealthcare.norm = rbind(cbind("Diabetes"=rep(0,251),
                                 "AnyHealthcare"=BOOT.norm[["AnyHealthcare"]][[1]]$mean),
                    cbind("Diabetes"=rep(1,251),
                          "AnyHealthcare"=BOOT.norm[["AnyHealthcare"]][[2]]$mean),
                    cbind("Diabetes"=rep(2,251),
                          "AnyHealthcare"=BOOT.norm[["AnyHealthcare"]][[3]]$mean))
AnyHealthcare.norm = as.data.frame(AnyHealthcare.norm)
AnyHealthcare.norm$Diabetes = as.factor(AnyHealthcare.norm$Diabetes)

AnyHealthcare.norm.CIspace = seq(1, 15, length.out=3)
AnyHealthcare_norm_plot = ggplot() +
  geom_histogram(aes(x=AnyHealthcare.norm$AnyHealthcare, y=..count../sum(..count..)*100,
                     fill=AnyHealthcare.norm$Diabetes), position="identity", bins=35) +
  geom_segment(aes(x=norm_AnyHealthcare_table$lower, xend=norm_AnyHealthcare_table$upper,
                   y=AnyHealthcare.norm.CIspace, yend=AnyHealthcare.norm.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=norm_AnyHealthcare_table$mean, xend=norm_AnyHealthcare_table$mean,
                   y=AnyHealthcare.norm.CIspace-0.8, yend=AnyHealthcare.norm.CIspace+0.8),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Normal CI on AnyHealthcare", fill="Diabetes",
       x="AnyHealthcare", y="Frequency")

#########################
AnyHealthcare.stud = rbind(cbind("Diabetes"=rep(0,251),
                                 "AnyHealthcare"=BOOT.stud[["AnyHealthcare"]][[1]]$mean),
                           cbind("Diabetes"=rep(1,251),
                                 "AnyHealthcare"=BOOT.stud[["AnyHealthcare"]][[2]]$mean),
                           cbind("Diabetes"=rep(2,251),
                                 "AnyHealthcare"=BOOT.stud[["AnyHealthcare"]][[3]]$mean))
AnyHealthcare.stud = as.data.frame(AnyHealthcare.stud)
AnyHealthcare.stud$Diabetes = as.factor(AnyHealthcare.stud$Diabetes)

AnyHealthcare.stud.CIspace = seq(1, 15, length.out=3)
AnyHealthcare_stud_plot = ggplot() +
  geom_histogram(aes(x=AnyHealthcare.stud$AnyHealthcare, y=..count../sum(..count..)*100,
                     fill=AnyHealthcare.stud$Diabetes),
                 position="identity", bins=35) +
  geom_segment(aes(x=stud_AnyHealthcare_table$lower, xend=stud_AnyHealthcare_table$upper,
                   y=AnyHealthcare.stud.CIspace, yend=AnyHealthcare.stud.CIspace),
               color=c("red", "green","blue"), fill="black", size=1) +
  geom_segment(aes(x=stud_AnyHealthcare_table$mean, xend=stud_AnyHealthcare_table$mean,
                   y=AnyHealthcare.stud.CIspace-0.8, yend=AnyHealthcare.stud.CIspace+0.8),
               color=c("red", "green","blue"), size=0.75) +
  labs(title="Student-t CI on AnyHealthcare", fill="Diabetes",
       x="AnyHealthcare", y="Frequency")

AnyHealthcare_norm_plot + AnyHealthcare_stud_plot + plot_layout(ncol = 2, guides = "collect")
```

## Normal and Student-t Bootstrap Analysis

 - Across all factors, we saw that the Normal CIs were much smaller than Student-t CIs
 - Each factor had about a normal distribution of means
 - 26 minutes!! 

```{r functions, message=FALSE, warning=FALSE, include=FALSE}
set.seed(26)
f1 <- function(data, m,n){

  bootstrap_data <- list()
  for(i in 1:m){
    temp_sample_ind <- sample(1:length(data), n,replace=TRUE)
    bootstrap_data[[i]] <- data[temp_sample_ind]
  }
  return(bootstrap_data)
}

b_means <- function(data,m){
  
  bootstrap_means <- rep(0,m)
  for(row in 1:m){
    row_vector <- data[[row]]
    bootstrap_means[row] <- mean(row_vector)
  }
  return(bootstrap_means)
}
b_sds <- function(data,m){
  
  bootstrap_sds <- rep(0,m)
  for(row in 1:m){
    row_vector <- data[[row]]
    bootstrap_sds[row] <- sd(row_vector)
  }
  return(bootstrap_sds)
}

a_est <- function(data,theta_hat){
  n <- length(data)
  I <- rep(NA, n)
for(i in 1:n){
   #Remove ith data point
   xnew <- data[-i]
   #Estimate theta
   theta_jack <- mean(xnew)
   I[i] <- (n-1)*(theta_hat - theta_jack)
}
#Estimate a
  a_hat <- (sum(I^3)/sum(I^2)^1.5)/6
  return(a_hat)
}


bca_CI <- function(theta_boot,theta_hat,m){

  alpha <- 0.05
  u <- c(alpha/2, 1-alpha/2) 
  z0 <- qnorm(mean(theta_boot <= theta_hat))
  zu <- qnorm(u)
  a <- 0
  #because the sample size of our data set is so large, the computation
  #is too intensive for rstudio to conduct. With such a large data set a should
  #be close to zero anyways, so I elected to choose zero. 
  
  u_adjusted <- pnorm(z0 + (z0+zu)/(1-a*(z0+zu)))
  #u_adjusted <- pnorm(z0 + (z0+zu)/(1-a_approx*(z0+zu))) 
  conf_int <- quantile(theta_boot,u_adjusted)
  return(conf_int)
  
}

bca_compile <- function(data0,data1,data2,theta_hat1,theta_hat2,theta_hat3,m,n){
  data.stats = setNames(data.frame(matrix(ncol = 12, nrow = length(m)*length(n))),
                 c("mean1", "sd1","ci_1_lower","ci_1_upper","mean2", "sd2","ci_2_lower","ci_2_upper","mean3", "sd3","ci_3_lower","ci_3_upper"))
  row.names(data.stats) <- c("m5,n10","m5,n25","m5,n75","m5,n125","m5,n250","m10,n10","m10,n25","m10,n75","m10,n125","m10,n250","m15,n10","m15,n25","m15,n75","m15,n125","m15,n250","m30,n10","m30,n25","m30,n75","m30,n125","m30,n250","m50,n10","m50,n25","m50,n75","m50,n125","m50,n250")
  counter=1
  bca_CI_means <- data.frame(matrix(ncol=3,nrow=m[5]))
  for(r in 1:length(m)){
    for(c in 1:length(n)){
      b0 <- f1(data0,m[r],n[c])
      b0_mean <- b_means(b0,m[r])
      b0_se <- b_sds(b0,m[r])
  
      b1 <- f1(data1,m[r],n[c])
      b1_mean <- b_means(b1,m[r])
      b1_se <- b_sds(b1,m[r])
      
      b2<- f1(data2,m[r],n[c])
      b2_mean <- b_means(b2,m[r])
      b2_se <- b_sds(b2,m[r])
  
      # b_mean_diff <- rep(NA,m[r])
      # b_se_diff <- rep(NA,m[r])
      # for(i in 1:m[r]){
      #   b_mean_diff[i] <- b0_mean[i]-b1_mean[i]
      #   b_se_diff[i] <- b0_se[i]-b1_se[i]
      # }
      # b_theta_hat_diff <- theta_hat1-theta_hat2
      # 
      # 
      # 
      # b_ci_diff <- bca_CI(b_mean_diff,b_theta_hat_diff,m[r])
      b0_ci <- bca_CI(b0_mean,theta_hat1,m[r])
      b1_ci <- bca_CI(b1_mean,theta_hat2,m[r])
      b2_ci <- bca_CI(b2_mean,theta_hat3,m[r])
      
      data.stats[counter,] <- c(mean(b0_mean),mean(b0_se),b0_ci[1],b0_ci[2],mean(b1_mean),mean(b1_se),b1_ci[1],b1_ci[2],mean(b2_mean),mean(b2_se),b2_ci[1],b2_ci[2])
      counter <- counter + 1
      if(m[r] == 50 & n[c] == 250){
        bca_CI_means[,1] <- b0_mean
        bca_CI_means[,2] <- b1_mean
        bca_CI_means[,3] <- b2_mean
        
      }
    }
  }
  
  
  return(list(data.stats,bca_CI_means))
  
}
```




```{r,echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
diab.data1<- read_csv("../../data/diabetes_012_health_indicators_BRFSS2015.csv")
nodib <- diab.data1 |> 
  filter(Diabetes_012==0)|>
  select(HighBP, HighChol, BMI, AnyHealthcare, GenHlth, Income)

predib <- diab.data1 |>
  filter(Diabetes_012==1)|>
  select(HighBP, HighChol, BMI, AnyHealthcare, GenHlth, Income)

dib <- diab.data1 |>
  filter(Diabetes_012==2)|>
  select(HighBP, HighChol, BMI, AnyHealthcare, GenHlth, Income)

m_vec <- c(5,10,15,30,50)
n_vec <- c(10,25,75,125,250)

# highBP <- c(nodib$HighBP,predib$HighBP,dib$HighBP)
# highBPlabel <- c(rep("no_diab",length(nodib$HighBP)),rep("pre_diab",length(predib$HighBP)),rep("diab",length(dib$HighBP)))
# hBP_frame <- data.frame(highBP, group = highBPlabel)
# 
# highChol <- c(nodib$HighChol,predib$HighChol,dib$HighChol)
# highChollabel <- c(rep("no_diab",length(nodib$HighChol)),rep("pre_diab",length(predib$HighChol)),rep("diab",length(dib$HighChol)))
# hChol_frame <- data.frame(highChol, group = highChollabel)
# 
# BMI <- c(nodib$BMI,predib$BMI,dib$BMI)
# BMIlabel <- c(rep("no_diab",length(nodib$BMI)),rep("pre_diab",length(predib$BMI)),rep("diab",length(dib$BMI)))
# BMI_frame <- data.frame(highBP, group = highBPlabel)
# 
# AnyHealthcare <- c(nodib$AnyHealthcare,predib$AnyHealthcare,dib$AnyHealthcare)
# AnyHealthcarelabel <- c(rep("no_diab",length(nodib$AnyHealthcare)),rep("pre_diab",length(predib$AnyHealthcare)),rep("diab",length(dib$AnyHealthcare)))
# AnyHealthcare_frame <- data.frame(AnyHealthcare, group = AnyHealthcarelabel)
# 
# GenHlth <- c(nodib$GenHlth,predib$GenHlth,dib$GenHlth)
# GenHlthlabel <- c(rep("no_diab",length(nodib$GenHlth)),rep("pre_diab",length(predib$GenHlth)),rep("diab",length(dib$GenHlth)))
# GenHlth_frame <- data.frame(GenHlth, group = GenHlthlabel)
# 
# Income <- c(nodib$Income,predib$Income,dib$Income)
# Incomelabel <- c(rep("no_diab",length(nodib$Income)),rep("pre_diab",length(predib$Income)),rep("diab",length(dib$Income)))
# Income_frame <- data.frame(Income, group = Incomelabel)
nodibindic <- rep("No Diabetes",50)
predibindic <- rep("Pre Diabetes",50)
dibindic <- rep("Diabetes",50)
indic <- c(nodibindic,predibindic,dibindic)



a <- bca_compile(nodib$HighBP,predib$HighBP,dib$HighBP,mean(nodib$HighBP),mean(predib$HighBP),mean(dib$HighBP),m_vec,n_vec)
a1 <- a[[1]]
a2 <- a[[2]]
highBP <- c(a2[,1],a2[,2],a2[,3])
#a3 <- cbind(a3,indic)
a3 <- data.frame(highBP,group=indic)

b <- bca_compile(nodib$HighChol,predib$HighChol,dib$HighChol,mean(nodib$HighChol),mean(predib$HighChol),mean(dib$HighChol),m_vec,n_vec)
b1 <- b[[1]]
b2 <- b[[2]]
highChol <- c(b2[,1],b2[,2],b2[,3])
b3 <- data.frame(highChol,group = indic)

c <- bca_compile(nodib$BMI,predib$BMI,dib$BMI,mean(nodib$BMI),mean(predib$BMI),mean(dib$BMI),m_vec,n_vec)
c1 <- c[[1]]
c2 <- c[[2]]
BMI <- c(c2[,1],c2[,2],c2[,3])
c3 <- data.frame(BMI,group=indic)

d <- bca_compile(nodib$AnyHealthcare,predib$AnyHealthcare,dib$AnyHealthcare,mean(nodib$AnyHealthcare),mean(predib$AnyHealthcare),mean(dib$AnyHealthcare),m_vec,n_vec)
d1 <- d[[1]]
d2 <- d[[2]]
AnyHealthcare <- c(d2[,1],d2[,2],d2[,3])
d3 <- data.frame(AnyHealthcare,group=indic)

e <- bca_compile(nodib$GenHlth,predib$GenHlth,dib$GenHlth,mean(nodib$GenHlth),mean(predib$GenHlth),mean(dib$GenHlth),m_vec,n_vec)
e1 <- e[[1]]
e2 <- e[[2]]
GenHlth <- c(e2[,1],e2[,2],e2[,3])
e3 <- data.frame(GenHlth,group=indic)

f <- bca_compile(nodib$Income,predib$Income,dib$Income,mean(nodib$Income),mean(predib$Income),mean(dib$Income),m_vec,n_vec)
f1 <- f[[1]]
f2 <- f[[2]]
Income <- c(f2[,1],f2[,2],f2[,3])
f3 <- data.frame(Income,group=indic)

#for m=50, n=250
#x02[3,25] is the lower bound of first CI
#x02[4,25] is the upper bound of first CI
#x02[7,25] is the lower bound of first CI
#x02[8,25] is the upper bound of first CI


make_table <- function(data){
  t = setNames(data.frame(matrix(ncol = 4, nrow = 3)), c("Mean", "SD","CI_Low","CI_High"))
  row.names(t) <- c("No Diabetes","Pre Diabetes","Diabetes")
  t[1,1] = data[25,1]
  t[2,1] = data[25,5]
  t[3,1] = data[25,9]
  
  t[1,2] = data[25,2]
  t[2,2] = data[25,6]
  t[3,2] = data[25,10]
  
  t[1,3] = data[25,3]
  t[2,3] = data[25,7]
  t[3,3] = data[25,11]
  
  t[1,4] = data[25,4]
  t[2,4] = data[25,8]
  t[3,4] = data[25,12]
  
  return(t)
}
make_table2 <- function(data){
  t = setNames(data.frame(matrix(ncol = 4, nrow = 3)), c("Mean", "SD","CI_Low","CI_High"))
  row.names(t) <- c("No Diabetes","Pre Diabetes","Diabetes")
  t[1,1] = data[1,1]
  t[2,1] = data[1,5]
  t[3,1] = data[1,9]
  
  t[1,2] = data[1,2]
  t[2,2] = data[1,6]
  t[3,2] = data[1,10]
  
  t[1,3] = data[1,3]
  t[2,3] = data[1,7]
  t[3,3] = data[1,11]
  
  t[1,4] = data[1,4]
  t[2,4] = data[1,8]
  t[3,4] = data[1,12]
  
  return(t)
}




```
##                        Caedon BCa bootstrap






Bias Corrected and Accelerated Confidence Intervals

Early struggles + acceleration constant

BCa by hand

Histograms + BCa confidence intervals

    
    
                            

##                          BCa by hand



I used the equation:

$g(u) = \hat{F}^{-1}(\phi(z_0 + \frac{z_0 + z_u}{1-a(z_0+z_u)}))$

  Lower bound = $g(\alpha/2)$, Upper bound = $g(1-\alpha/2)$
  $\phi$ is the standard normal cdf 
  $\hat{F}$ is the bootstrap cdf
  $z_0 = \phi^{-1}F(\hat{\theta})$, quantile of mean of theta_boot <= theta_hat
  $z_u = \phi^{-1}(u)$, quantiles of our desired bounds 
  
$\hat{a} = \frac{1}{6}\frac{\sum_{i=1}^n I_i^3}{(\sum_{i=1}^n I_i^2)^{3/2}}$
  
$I_i = (n-1)(\hat{\theta}-\hat{\theta}_{-i})$ finite sample jacknife approx.



##                       BCa High Blood Pressure
```{r highBP plot, echo=FALSE, fig.height=3.5, fig.width=9, message=FALSE, warning=FALSE}

highBPtable <- make_table(a1)
highBPtable2 <- make_table2(a1)
highBPtable.kable <- kable(highBPtable, caption = "High Blood Pressure m=50 n=250", digits = 3, format = "html") %>%
kable_styling(full_width=TRUE,position="float_left") %>% column_spec(1:5,width="3em")
highBPtable.kable2 <- kable(highBPtable2, caption = "High Blood Pressure m=5 n=10", digits = 3, format = "html") %>% kable_styling(full_width=TRUE,position="center") %>% column_spec(1:5,width="3em")

highBPplot <- ggplot(data=a3,aes(x = highBP,fill = group))+
  geom_histogram(bins=40)+
  geom_segment(aes(x=(a1[25,3]),y=15,xend=(a1[25,4]),yend=15),col="Green")+
  geom_segment(aes(x=(a1[1,3]),y=13,xend=(a1[1,4]),yend=13,),col="Green")+
  geom_segment(aes(x=(a1[25,7]),y=11,xend=(a1[25,8]),yend=11),col = "Blue")+
  geom_segment(aes(x=(a1[1,7]),y=9,xend=(a1[1,8]),yend=9),col = "Blue")+
  geom_segment(aes(x=(a1[25,11]),y=7,xend=(a1[25,12]),yend=7), col = "Red")+
  geom_segment(aes(x=(a1[1,11]),y=5,xend=(a1[1,12]),yend=5),col = "Red")+
  labs(fill="Diabetes")

highBPtable.kable
highBPtable.kable2
highBPplot
  
```

##                      BCa High Cholesterol
```{r High Cholesterol, echo=FALSE, fig.height=3.5, fig.width=9, message=FALSE, warning=FALSE}
highCholtable <- make_table(b1)
highCholtable2 <- make_table2(b1)
highCholtable.kable <- kable(highCholtable, caption = "High Cholesterol m=50 n=250", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="float_left") %>% column_spec(1:5,width="3em")
highCholtable.kable2 <- kable(highCholtable2, caption = "High Cholesterol m=5 n=10", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="center") %>% column_spec(1:5,width="3em")

highCholplot <- ggplot(data=b3,aes(x = highChol,fill = group))+
  geom_histogram(bins=40)+
  geom_segment(aes(x=(b1[25,3]),y=15,xend=(b1[25,4]),yend=15),col = "Green")+
  geom_segment(aes(x=(b1[1,3]),y=13,xend=(b1[1,4]),yend=13),col = "Green")+
  geom_segment(aes(x=(b1[25,7]),y=11,xend=(b1[25,8]),yend=11),col = "Blue")+
  geom_segment(aes(x=(b1[1,7]),y=9,xend=(b1[1,8]),yend=9),col = "Blue")+
  geom_segment(aes(x=(b1[25,11]),y=7,xend=(b1[25,12]),yend=7), col = "Red")+
  geom_segment(aes(x=(b1[1,11]),y=5,xend=(b1[1,12]),yend=5), col = "Red")+
  labs(fill="Diabetes")

highCholtable.kable
highCholtable.kable2
highCholplot
```

##                              BCa BMI
```{r BMI, echo=FALSE, fig.height=3.5, fig.width=9, message=FALSE, warning=FALSE}
BMItable <- make_table(c1)
BMItable2 <- make_table2(c1)
BMItable.kable <- kable(BMItable, caption = "BMI m=50 n=250", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="float_left") %>% column_spec(1:5,width="3em")
BMItable.kable2 <- kable(BMItable2, caption = "BMI m=5 n=10", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="center") %>% column_spec(1:5,width="3em")

BMIplot <- ggplot(data=c3,aes(x = BMI,fill = group))+
  geom_histogram(bins=40)+
  geom_segment(aes(x=(c1[25,3]),y=15,xend=(c1[25,4]),yend=15),col = "Green")+
  geom_segment(aes(x=(c1[1,3]),y=13,xend=(c1[1,4]),yend=13),col = "Green")+
  geom_segment(aes(x=(c1[25,7]),y=11,xend=(c1[25,8]),yend=11),col = "Blue")+
  geom_segment(aes(x=(c1[1,7]),y=9,xend=(c1[1,8]),yend=9),col = "Blue")+
  geom_segment(aes(x=(c1[25,11]),y=7,xend=(c1[25,12]),yend=7), col = "Red")+
  geom_segment(aes(x=(c1[1,11]),y=5,xend=(c1[1,12]),yend=5), col = "Red")+
  labs(fill="Diabetes")

BMItable.kable
BMItable.kable2
BMIplot
```

##                          BCa Any Healthcare
```{r Any Healthcare, echo=FALSE, fig.height=3.5, fig.width=9, message=FALSE, warning=FALSE}
AnyHealthcaretable <- make_table(d1)
AnyHealthcaretable2 <- make_table2(d1)
AnyHealthcare.kable <- kable(AnyHealthcaretable, caption = "Any Healthcare m=50 n=250", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="float_left") %>% column_spec(1:5,width="3em")
AnyHealthcare.kable2 <- kable(AnyHealthcaretable2, caption = "Any Healthcare m=5 n=10", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="center") %>% column_spec(1:5,width="3em")

AnyHealthcareplot <- ggplot(data=d3,aes(x = AnyHealthcare,fill = group))+
  geom_histogram(bins=40)+
  geom_segment(aes(x=(d1[25,3]),y=15,xend=(d1[25,4]),yend=15),col = "Green")+
  geom_segment(aes(x=(d1[1,3]),y=13,xend=(d1[1,4]),yend=13),col = "Green")+
  geom_segment(aes(x=(d1[25,7]),y=11,xend=(d1[25,8]),yend=11),col = "Blue")+
  geom_segment(aes(x=(d1[1,7]),y=9,xend=(d1[1,8]),yend=9),col = "Blue")+
  geom_segment(aes(x=(d1[25,11]),y=7,xend=(d1[25,12]),yend=7), col = "Red")+
  geom_segment(aes(x=(d1[1,11]),y=5,xend=(d1[1,12]),yend=5), col = "Red")+
  labs(fill="Diabetes")

AnyHealthcare.kable
AnyHealthcare.kable2
AnyHealthcareplot
```

##                          BCa General Health
```{r General Health, echo=FALSE, fig.height=3.5, fig.width=9, message=FALSE, warning=FALSE}
GenHlthtable <- make_table(e1)
GenHlthtable2 <- make_table2(e1)
GenHlth.kable <- kable(GenHlthtable, caption = "General Health m=50 n=250", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="float_left") %>% column_spec(1:5,width="3em")
GenHlth.kable2 <- kable(GenHlthtable2, caption = "General Health m=5 n=10", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="center") %>% column_spec(1:5,width="3em")

GenHlthplot <- ggplot(data=e3,aes(x = GenHlth,fill = group))+
  geom_histogram(bins=40)+
  geom_segment(aes(x=(e1[25,3]),y=15,xend=(e1[25,4]),yend=15),col = "Green")+
  geom_segment(aes(x=(e1[1,3]),y=13,xend=(e1[1,4]),yend=13),col = "Green")+
  geom_segment(aes(x=(e1[25,7]),y=11,xend=(e1[25,8]),yend=11),col = "Blue")+
  geom_segment(aes(x=(e1[1,7]),y=9,xend=(e1[1,8]),yend=9),col = "Blue")+
  geom_segment(aes(x=(e1[25,11]),y=7,xend=(e1[25,12]),yend=7), col = "Red")+
  geom_segment(aes(x=(e1[25,11]),y=5,xend=(e1[25,12]),yend=5), col = "Red")+
  labs(fill="Diabetes")

GenHlth.kable
GenHlth.kable2
GenHlthplot
```

##                             BCa Income
```{r Income, echo=FALSE, fig.height=3.5, fig.width=9, message=FALSE, warning=FALSE}
Incometable <- make_table(f1)
Incometable2 <- make_table2(f1)
Income.kable <- kable(GenHlthtable, caption = "Income m=50 n=250", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="float_left") %>% column_spec(1:5,width="3em")
Income.kable2 <- kable(GenHlthtable2, caption = "Income m=5 n=10", digits = 3, format = "html")%>% kable_styling(full_width=TRUE,position="center") %>% column_spec(1:5,width="3em")

Incomeplot <- ggplot(data=f3,aes(x = Income,fill = group))+
  geom_histogram(bins=40)+
  geom_segment(aes(x=(f1[25,3]),y=15,xend=(f1[25,4]),yend=15),col = "Green")+
  geom_segment(aes(x=(f1[1,3]),y=13,xend=(f1[1,4]),yend=13),col = "Green")+
  geom_segment(aes(x=(f1[25,7]),y=11,xend=(f1[25,8]),yend=11),col = "Blue")+
  geom_segment(aes(x=(f1[1,7]),y=9,xend=(f1[1,8]),yend=9),col = "Blue")+
  geom_segment(aes(x=(f1[25,11]),y=7,xend=(f1[25,12]),yend=7), col = "Red")+
  geom_segment(aes(x=(f1[1,11]),y=5,xend=(f1[1,12]),yend=5), col = "Red")+
  labs(fill="Diabetes")

Income.kable
Income.kable2
Incomeplot
```

## Conclusion

```{r Conclusion1, echo=FALSE, message=FALSE, warning=FALSE}
algos.names = c("Percentile", "Basic", "Normal", "Student-t", "BCa")

#####################################################
conc_table_np = rbind("Income"=c(T,T,T,F,T),
                      "BMI"=c(T,T,T,T,T),
                      "GenHlth"=c(T,T,T,F,T),
                      "HighBP"=c(T,T,T,F,T),
                      "Hlthcare"=c(F,F,F,F,F),
                      "HighChol"=c(T,T,T,T,T))
colnames(conc_table_np) = algos.names
conc_table_np = t(conc_table_np)
conc_kable_np = kable(conc_table_np, caption="No-Pre Difference in Means", format = "html") %>%
  kable_styling(full_width=F, position="float_left", font_size=10) %>%
  row_spec(0, bold=T, font_size=14) %>% row_spec(0:5, align="c") %>%
  column_spec(1, bold = TRUE, border_right = TRUE, width="6em")

#####################################################
conc_table_pd = rbind("Income"=c(T,T,F,F,T),
                      "BMI"=c(T,T,T,T,F),
                      "GenHlth"=c(T,T,T,F,T),
                      "HighBP"=c(T,T,T,T,F),
                      "Hlthcare"=c(T,F,T,F,F),
                      "HighChol"=c(T,T,T,F,F))
colnames(conc_table_pd) = algos.names
conc_table_pd = t(conc_table_pd)
conc_kable_pd = kable(conc_table_pd, caption="Pre-Diab Difference in Means",
                      format = "html") %>%
  kable_styling(full_width=F, position="left", font_size=10) %>%
  row_spec(0, bold=T, font_size=14) %>% row_spec(0:5, align="c") %>%
  column_spec(1, bold = TRUE, border_right = TRUE, width="6em")

#####################################################
conc_table_nd = rbind("Income"=c(F,T,T,F,T),
                      "BMI"=c(T,T,T,F,T),
                      "GenHlth"=c(T,T,T,F,T),
                      "HighBP"=c(T,T,T,F,T),
                      "Hlthcare"=c(T,T,T,T,F),
                      "HighChol"=c(T,T,T,F,T))
colnames(conc_table_nd) = algos.names
conc_table_nd = t(conc_table_nd)
conc_kable_nd = kable(conc_table_nd, caption="No-Diab Difference in Means",
                      format = "html") %>%
  kable_styling(full_width=F, position="center", font_size=10) %>%
  row_spec(0, bold=T, font_size=14) %>% row_spec(0:5, align="c") %>%
  column_spec(1, bold = TRUE, border_right = TRUE, width="6em")
```

```{r Conclusion2, echo=FALSE, message=FALSE, warning=FALSE}
conc_kable_np
conc_kable_pd
conc_kable_nd
```

